FoRTE baseline

### 2019-07-22 analysis/paper/paper.Rmd
Improve parameter subset LAI TS figure and text

```{r pairs-time, fig.cap = pairs_time_cap, fig.dim = c(8, 8)}
pairs_time_cap <- paste(
  htmlfig(),
  "Post-1975 growing season averaged NPP vs. LAI, with observation (in black)",
  "and linear regression, by model type."
)
readd(pairs_time_averaged)
```

In most simulations, the leaf area index was usually too low relative for a given level of net primary productivity, but the relationship between these two variables varied with model configuration (Figure 3).
The crown model (closed vs. finite) had the strongest effect: Compared to the simulations with "closed" crowns, simulations with finite canopy radius generally had lower net primary productivity for the same leaf area index.
Only a few simulations matched _both_ the observed leaf area index and net primary productivity, and all of them had the finite canopy radius configuration.

```{r bigfacet-plot, fig.cap = bigfacet_cap, fig.dim = c(12, 8)}
bigfacet_cap <- paste(
  htmlfig(),
  "ED-2.2 PFT-level predictions of leaf area index (LAI) by model configuration and parameterization."
)
readd(lai_pft_plot)
```

@@

Different parameter combinations led to model outputs that had not only different bulk ecosystem properties but also qualitatively different plant communities (Figure 3).
The most common outcome was immediate and persistent dominance by early hardwood trees, though in some cases, early hardwoods co-existed with late hardwood or pine.
<!-- TODO Probably need to do a different analysis here. Maybe look at all the outputs, identify several different "ecological scenarios", and then analyze the fraction of runs that experienced those probabilities? -->

>>>>

```{r pairs-time, fig.cap = pairs_time_cap, fig.dim = c(8, 8)}
pairs_time_cap <- paste(
  htmlfig(),
  "Post-1975 growing season averaged NPP vs. LAI, with observation (in black)",
  "and linear regression, by model type.",
  "Letter labels are selected runs with the same parameters,",
  "and match the rows in Figure 4. The characteristics of these poitns are",
  "as follows:",
  "(A) high NPP and LAI, and relatively high pine LAI;",
  "(B) high Shannon diversity;",
  "(C) close to observed NPP and LAI values;",
  "(D) high early hardwood LAI",
  "(E) high late hardwood LAI."
)
readd(pairs_time_averaged)
```

In most simulations, the leaf area index was usually too low for a given level of net primary productivity, but the relationship between these two variables varied with model configuration (Figure 3).
The crown model (closed vs. finite) had the strongest effect: Compared to the simulations with "closed" crowns, simulations with finite canopy radius generally had lower net primary productivity for the same leaf area index.
Only a few simulations matched _both_ the observed leaf area index and net primary productivity, and all of them had the finite canopy radius configuration.

```{r bigfacet-plot, fig.cap = bigfacet_cap, fig.dim = c(12, 8)}
bigfacet_cap <- paste(
  htmlfig(),
  "PFT-level predictions of leaf area index (LAI) by model configuration and parameterization.",
  "Each row of plots is a simulation with the same set of parameters across model configurations.",
  "Letters correspond to the labels in Figure 3."
)
readd(lai_pft_plot)
```

@@

Model structure and parameters interacted in determining the community assembly and dynamics of each simulation (Figure 4).
Generally, the highest net primary productivity and leaf area index values (averaged across growing seasons from 1975 to 2000) occurred in runs dominated by pine.
With the exception of the configuration with finite canopy radius and two-stream radiative transfer (under which most simulations had near-zero productivity), parameter values were more important to determining the ecological trajectory than model configuration.
For example, all model configurations in parameter combination _E_ saw immediate and total dominance by late hardwood followed by eventual die-off.
However, the magnitude of peak leaf area index and the pace of the subsequent die-off varied with model configuration, with a smaller peak and slower die-off under a finite canopy compared to the default closed canopy.
